Recruiting Chapter

### 2020-12-19 manuscript.Rmd
draft changes manuscript

---
title: "Recruiting Chapter"
author: "Ozan Jaquette"
bibliography: ./other/burd_recruiting_chapter.bib
output: 
  bookdown::pdf_document2:
    toc: FALSE
csl: ./other/apa.csl
urlcolor: blue
header-includes:
      - \usepackage{pdflscape}
      - \usepackage{geometry}
      - \usepackage{floatrow}
      - \floatsetup{capposition=top}
---

@@

Our project collected data on off-campus recruiting visits made in 2017 by a convenience sample of colleges and universities. Our analysis sample is based on three different lists of postsecondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102); all private universities in the top 100 of U.S. News and World Report National Universities rankings (N=58); and all private colleges in the top 50 of U.S. News and World Report Liberal Arts Colleges rankings (N=47). For each of these institutions, we investigated their admissions website for pages that provided the details of upcoming off-campus recruiting visits. For institutions that posted such pages, we scraped the pages once per week throughout the 2017 calendar year. Many colleges and university only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools). These institutions are excluded from the analyses. Our final analysis sample consists of 17 public research universities, 13 private research universities, and 12 private liberal arts colleges. <!--[MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]-->

>>>>

---
title: "Recruiting Chapter"
author: 
  - Ozan Jaquette
  - Crystal Han
  - Irma Castaneda
bibliography: ./other/burd_recruiting_chapter.bib
output: 
  bookdown::pdf_document2:
    toc: FALSE
csl: ./other/apa.csl
urlcolor: blue
header-includes:
      - \usepackage{pdflscape}
      - \usepackage{geometry}
      - \usepackage{floatrow}
      - \floatsetup{capposition=top}
---

@@

[CRYSTAL, CAN YOU CLEAN UP THIS PARAGRAPH AND THE NEXT ONE; THESE PARAGRAPHS ARE TRANSITIONING FROM LIT REVIEW INTRODUCTION/BACKGROUND TO OUR PROJECT; AND ALSO MOTIVATING THE ANELYSES THAT WE DO; JUST USE YOUR JUDGMENT. THANK YOU!] Our project collected data on off-campus recruiting visits made in 2017 by a convenience sample of colleges and universities. Our analysis sample is based on three different lists of postsecondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102); all private universities in the top 100 of U.S. News and World Report National Universities rankings (N=58); and all private colleges in the top 50 of U.S. News and World Report Liberal Arts Colleges rankings (N=47). For each of these institutions, we investigated their admissions website for pages that provided the details of upcoming off-campus recruiting visits. For institutions that posted such pages, we scraped the pages once per week throughout the 2017 calendar year. Many colleges and university only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools). These institutions are excluded from the analyses. Our final analysis sample consists of 17 public research universities, 13 private research universities, and 12 private liberal arts colleges. <!--[MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]-->
